---
params: 
  prjName: "State Name"
title: "COVID-19 Case and Death Rates"
subtitle: "State of `r params$prjName`"
output: 
  word_document:
    reference_docx: "Templates/Word-Template-00.docx"
date: "`r paste('As of:',Sys.Date())`"
---

```{r input, include=FALSE}
readname = function()# Get the project name
{
  params$prjName
}
prjName=readname()
```

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
library(flextable)
library(officer)
library(janitor)
library(Rcpp)

covid<-read.csv("Input_Data/covid.csv")

wa_pop<-read.csv("Input_Data/WA Population.csv",fileEncoding = 'UTF-8-BOM')
wa_pop<-wa_pop %>%
  rowwise() %>%
  mutate(Pop2020=as.numeric(gsub(",","",Pop2020)),Pop2021=as.numeric(gsub(",","",Pop2021))) %>%
  mutate(Population=round(mean(c(Pop2020,Pop2021)),digits = 0)) %>%
  select(-Pop2020,-Pop2021)  

wa_covid<-covid %>% filter(state=="Washington" & county != "Unknown") %>%
   mutate(Date=as.Date(date), FIPS=gsub("USA-","",geoid)) %>%
   rename(State=state, County=county, Cases=cases, Deaths=deaths, `Avg Cases`=cases_avg, `Avg Cases/100K`=cases_avg_per_100k, `Avg Deaths`=deaths_avg,
          `Avg Deaths/100K`=deaths_avg_per_100k) %>%
   select(Date, FIPS, everything(), -X, -date, -geoid)

wa_covid_cum<-wa_covid %>%
  group_by(County) %>%
  summarise(Cases=sum(Cases), Deaths=sum(Deaths)) %>%
  left_join(wa_pop, by=c("County"="County")) %>%
  adorn_totals("row",name="Total") %>%
  mutate(`Cases/100K`=round(Cases/Population*100000,digits = 0), `Deaths/100K`=round(Deaths/Population*100000,digits = 0))

```

# Introduction 

* Data for this report are Collected from [Newyork Times on Github](https://github.com/nytimes) 
  + The primary data published here are the daily number of cases and deaths reported in each county of Washington State since the beginning of the pandemic
* This time series data is compiled from state and local governments and health departments in an attempt to provide a complete view of the ongoing outbreak 
  + Because of the widespread shortage of testing, however, the data is necessarily limited in the picture it presents of the outbreak 

# Table-1: Cases and Deaths

```{r countyTable, ft.align='left', echo=FALSE, warning=FALSE, message=FALSE}

border_h<-fp_border(color = "grey")
border_v<-fp_border(color = "grey")

flextable(wa_covid_cum, theme_fun = theme_booktabs) %>%
  autofit() %>%
  border_inner_h(part = "all", border = border_h) %>%
  border_inner_v(part = "all", border = border_v) %>%
  bold(bold = TRUE, part = "header") %>%
  hline(i=nrow(wa_covid_cum)-1, border = fp_border(color="grey35", width=2))
  
```

## Fig-1: Cumulative Cases by County

```{r countyCases, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=15, fig.height=10}
###############################
#             fig-1           #
#           Cases Bar         #
###############################

ymax1 <- max(subset(wa_covid_cum,County!="Total")$Cases,na.rm = T) +10000

ggplot(wa_covid_cum %>% filter(County !="Total"), aes(x=reorder(County, -Cases), y=Cases)) +
  geom_bar(stat="identity",  fill="steelblue", width = 0.6) +
  geom_text(aes(label=Cases), vjust=0, hjust=-.5, parse=T, angle = 90) +
  theme_classic()+
  theme(text=element_text(size=15))+
  scale_y_continuous(limits = c(0, ymax1), breaks = seq(0, ymax1, by = 10000)) +
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("County") +
  ylab("Cumulative Cases") 

```

## Fig-2: Cumulative Deaths by County

```{r countyDeaths, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=15, fig.height=10}
###############################
#             fig-2           #
#          Deaths Bar         #
###############################

ymax1 <- max(subset(wa_covid_cum,County!="Total")$Deaths,na.rm = T) +50

ggplot(wa_covid_cum %>% filter(County !="Total"), aes(x=reorder(County, -Deaths), y=Deaths)) +
  geom_bar(stat="identity",  fill="steelblue", width = 0.6) +
  geom_text(aes(label=Deaths), vjust=0, hjust=-.5, parse=T, angle = 90) +
  theme_classic()+
  theme(text=element_text(size=15))+
  scale_y_continuous(limits = c(0, ymax1), breaks = seq(0, ymax1, by = 100)) +
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("County") +
  ylab("Cumulative Deaths") 

```

## Fig-3: Cumulative Cases Rate per 100,000 Population by County

```{r countyCasesRate, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=15, fig.height=10}
###############################
#             fig-3           #
#         Case Rate Bar       #
###############################

ymax1 <- max(subset(wa_covid_cum,County!="Total")$`Cases/100K`,na.rm = T) +1000

ggplot(wa_covid_cum %>% filter(County !="Total"), aes(x=reorder(County, -`Cases/100K`), y=`Cases/100K`)) +
  geom_bar(stat="identity",  fill="steelblue", width = 0.6) +
  geom_text(aes(label=`Cases/100K`), vjust=0, hjust=-.5, parse=T, angle = 90) +
  theme_classic()+
  theme(text=element_text(size=15))+
  scale_y_continuous(limits = c(0, ymax1), breaks = seq(0, ymax1, by = 1000)) +
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("County") +
  ylab("Cumulative Cases/100K Population") 

```

## Fig-4: Cumulative Cases Rate per 100,000 Population by County

```{r countyDeathRate, results='hide', echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=15, fig.height=10}
###############################
#             fig-4           #
#         Death Rate Bar      #
###############################

ymax1 <- max(subset(wa_covid_cum,County!="Total")$`Deaths/100K`,na.rm = T) +10

ggplot(wa_covid_cum %>% filter(County !="Total"), aes(x=reorder(County, -`Deaths/100K`), y=`Deaths/100K`)) +
  geom_bar(stat="identity",  fill="steelblue", width = 0.6) +
  geom_text(aes(label=`Deaths/100K`), vjust=0, hjust=-.5, parse=T, angle = 90) +
  theme_classic()+
  theme(text=element_text(size=15))+
  scale_y_continuous(limits = c(0, ymax1), breaks = seq(0, ymax1, by = 10)) +
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("County") +
  ylab("Cumulative Deaths/100K Population") 

```
